Estimating duration in the presence of misclassification

### 2024-07-29 transmission.tex
Rob p127 comment

\Cref{transmission:eq:forward-substitute} is derived from \cref{inc-prev:eq:EPt-matrix}: $\vec{P} = \matr{S} \vec{I}$.
For this to have a unique solution, $\vec{I}$ and $\vec{P}$ need the same dimension.
However, I am using a period of prevalence which starts after the first infections.
These prior infections will still contribute to the prevalence.
I assume that the incidence for $t \leq 1$ is constant.
Therefore, $P_1 = I_0 \sum_{i=1}^{\dmax} S(i)$ and $I_t = P_1 / \sum_{i=1}^{\dmax} S(i)$ for $t \leq 1$.

>>>>

\Cref{transmission:eq:forward-substitute} is derived from \cref{inc-prev:eq:EPt-matrix}: $\vec{P} = \matr{S} \vec{Z}$.
For this to have a unique solution, $\vec{Z}$ and $\vec{P}$ need the same dimension.
However, I am using a period of prevalence which starts after the first infections.
These prior infections will still contribute to the prevalence.
I assume that the incidence for $t \leq 1$ is constant.
Therefore, $P_1 = Z_0 \sum_{i=1}^{\dmax} S(i)$ and $Z_t = P_1 / \sum_{i=1}^{\dmax} S(i)$ for $t \leq 1$.
